Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-14 main.tex
latex tweaks of main files

@@

\begin{figure}[t]
\centering
\begin{tabular}{ccc}
  \begin{tikzpicture}
    % [line join=bevel,z={( 3.85mm, -3.85mm)}]
    [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]

@@

    \draw[line width=0.1cm] (O) -- (A) -- (E) -- cycle;
  \end{tikzpicture}
\end{tabular} 
\caption{From left to right: local patches around a vertex, and edge, and a triangle. The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\begin{tikzpicture}[rotate=-60]
    \coordinate (A) at (0,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (1,1.5);
    \coordinate (D) at (3,1.5); 
    \coordinate (E) at (3,3); 
    \coordinate (F) at (4,0.25); 
    \coordinate (X) at (1,-1.5);
    \coordinate (Y) at (3,-1.5); 
    \coordinate (T) at (5,2);

@@

    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET); 
\end{tikzpicture}
\end{center}
\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}
\label{figure:spanningtree}
\end{figure}

@@

\begin{figure}[h]
% \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
\centering
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,0.8); % Bottom right
    \coordinate (CR)  at ( 1,0.8); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \coordinate (ML) at  (-0.8,2.2);% ($(CL)!0.3!(Z)$);
    \coordinate (MR) at  ( 0.8,2.2);% ($(CR)!0.6!(Z)$);
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (ML) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (MR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (MR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (MR) -- cycle;
\end{tikzpicture}
\qquad
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,1); % Bottom right
    \coordinate (CR)  at ( 1,1); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CR) -- (CRR) -- cycle;
\end{tikzpicture}

\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}
\label{figure:not_manifold_triang}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \begin{tikzpicture}
        % Coordinates of the triangle
        \coordinate (A) at (0,0); % Vertex A = v_0
        \coordinate (B) at (4,0); % Vertex B = v_1
        \coordinate (C) at (1,3); % Vertex C = v_2
        \coordinate (M) at ($(A)!0.5!(B)$); % Midpoint M of AB
        % Heights from each vertex
        \coordinate (H_A) at ($(C)!(A)!(B)$); % Height from A to BC
        \coordinate (H_B) at ($(C)!(B)!(A)$); % Height from B to AC
        \coordinate (H_C) at ($(A)!(C)!(B)$); % Height from C to AB
        \coordinate (H_M) at ($(B)!(M)!(C)$); % Height from M to BC
        % Drawing the triangle
        \draw[thick] (A) -- (B) -- (C) -- cycle;
        % Drawing the bisector from C to AB and the height vectors 
        %\draw[dashed] (C) -- (M);
        \draw[] (C) -- (M);
        \draw[dashed,->,line width=1.0pt,>=latex] (H_A) -- (A); % Height vector from A, original 
        \draw[dashed,->,line width=1.0pt,>=latex] (H_M) -- (M); % Height vector from A, original 
        \draw[dashed,->,line width=1.0pt,>=latex] (H_C) -- (C); % Height vector from C, unaffected
        % Marking the height points
        \node[above right] at (C) {$v_2$};  
        \node[below left] at (A) {$v_0$};
        \node[below right] at (B) {$v_1$};
        \node[below] at (M) {$z_S$};
    \end{tikzpicture}
    \begin{tikzpicture}

@@

        % Marking the points
        \node[above right] at (C) {$v_2$};  
        \node[below left] at (A) {$v_0$};
        \node[below right] at (B) {$v_1$};
        \node[right] at (G) {$z_T$};
    \end{tikzpicture}
    \end{center}
    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
    the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
    The height vector to $v_2$ in all three triangles remains the same. The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle. 
    Right: 
    the triangle $T$ is trisected, leading to three new triangles. 
    The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \begin{tabular}{ccc}
    \begin{tikzpicture}
        % [line join=bevel,z={( 3.85mm, -3.85mm)}]
        [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]

@@

        \draw[dotted] (O) -- (A); % THIS ONE 
        \draw[dotted] (O) -- (B); % THIS ONE 
        \draw[] (A) -- (B); % THIS ONE 
%                 \draw (O) -- (C);
%                 \draw (O) -- (D);
%                 \draw (O) -- (E);
        \draw[line width=0.2em] (B) -- (C) -- (D) -- (E) -- (A);
    \end{tikzpicture}%
    \end{tabular} 
    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.
    The triangle $T$ completes the star around an interior vertex. $A$ is the complement of the triangle within the star. 
    $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
    $\Gamma_2$ is left invariant by the deformation.
    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
    and 
    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
    }\label{figure:geometricconstruction}
\end{figure}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{|l|c|c|c|}
        \hline
                                                  & $\grad$           & $\curl$           & $\divergence$   \\ \hline
        $\Gamma = F_0 \cup F_1 \cup F_2 \cup F_3$ & 0.0862501765      & 0.1453729386      & 0.2601720480    \\ \hline
        $\Gamma =          F_1 \cup F_2 \cup F_3$ & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
        $\Gamma =                   F_2 \cup F_3$ & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
        $\Gamma =                            F_3$ & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
        $\Gamma =                      \emptyset$ & 0.2631059409      & 0.1458215887      & 0.0874066554    \\ \hline
    \end{tabular}
    \caption{
    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
    where boundary conditions are imposed along the boundary part $\Gamma$, 
    computed via lowest-order finite element methods on a refined mesh. 
    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
    give the upper bound $2/\pi \cdot \diam(\Delta^3) \approx 0.90031631615$.
    }\label{table:referencepoincarefriedrichs}
\end{table}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio       & $\grad$ est   & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.904       & 2.842               & 0.904         & 2.842              & 0.225              & 1.339              &  5.953         \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381       & 2.896               & 1.421         & 1.729              & 0.322              & 2.505              &  7.781         \\
        \hline
        $\calT_{L'}$    & 0.822        & 2.391       & 2.909               & 2.391         & 2.909              & 0.322              & 4.053              & 12.587         \\
        \hline
        $\calT_{S,5}$   & 0.978        & 2.752       & 2.814               & 1.779         & 1.819              & 0.346              & 3.717              & 10.744         \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131       & 3.202               & 3.131         & 3.202              & 0.346              & 5.453              & 15.762         \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761       & 2.824               & 2.761         & 2.824              & 0.346              & 4.662              & 13.476         \\
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
\end{table}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est  & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
        \hline
        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
        \hline
        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
        \hline
        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
        \hline
        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
        \hline
    \end{tabular} 
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
\end{table}

\begin{table}[t]  
    \centering
    \begin{tabular}{|r||r|r|r||r|r|r|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio          & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310                & 0.183             & 3.391             & 18.453          \\
        \hline
        $\calT_{C,K}$   & 0.225        & 12.157      & 54.030                 & 0.183             & 25.899            & 140.920         \\
        \hline
        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056                & 0.233             & 152.886           & 655.993         \\
        \hline
        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655                & 0.233             & 512.273           & 2198.026        \\
        \hline
        $\calT_{F}$     & 0.554        & 25752.342   & 46403.302              & 0.310             & 8958.467          & 28835.266       \\ 
        \hline
    \end{tabular}
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
\end{table}

>>>>

\usepackage[colorlinks=true]{hyperref}         % For hypertext links
% Make the hyperlinks look similar to arXiv's
\hypersetup{
    colorlinks=true,
    linkcolor=Maroon,    % Color of internal links (sections)
    citecolor=red,    % Color of citations
    urlcolor=blue,     % Color for URLs
    urlbordercolor={1 1 1},
    pdfborder={0.5 0.5 0}  % Removes the border around the links
}

@@

\begin{figure}[t]
\caption{From left to right: local patches around a vertex, and edge, and a triangle. The local patch of any full-dimensional simplex only consists of that simplex itself (and its subsimplices).}\label{figure:patches}
\centering
\begin{tabular}{ccc}
  \begin{tikzpicture}
    % [line join=bevel,z={( 3.85mm, -3.85mm)}]
    [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]

@@

    \draw[line width=0.1cm] (O) -- (A) -- (E) -- cycle;
  \end{tikzpicture}
\end{tabular} 
\end{figure}

@@

\begin{figure}[t]
\caption{Face-connected triangulation of a domain. The arrows depict a spanning tree in the face-connection graph.}\label{figure:spanningtree}
\begin{center}
\begin{tikzpicture}[rotate=-60]
    \coordinate (A) at (0,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (1,1.5);
    \coordinate (D) at (3,1.5); 
    \coordinate (E) at (3,3); 
    \coordinate (F) at (4,0.25); 
    \coordinate (X) at (1,-1.5);
    \coordinate (Y) at (3,-1.5); 
    \coordinate (T) at (5,2);

@@

    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBDF) -- (CentroidDFT); 
    \draw[-latex, thick, shorten <=1.0pt, shorten >=2.0pt] (CentroidCDE) -- (CentroidDET); 
\end{tikzpicture}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\caption{Left: manifold triangulation of an annulus. Right: not a manifold triangulation.}\label{figure:not_manifold_triang}
% \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
\centering
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,0.8); % Bottom right
    \coordinate (CR)  at ( 1,0.8); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \coordinate (ML) at  (-0.8,2.2);% ($(CL)!0.3!(Z)$);
    \coordinate (MR) at  ( 0.8,2.2);% ($(CR)!0.6!(Z)$);
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (ML) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (MR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (MR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (MR) -- cycle;
\end{tikzpicture}
\qquad
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,1); % Bottom right
    \coordinate (CR)  at ( 1,1); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CR) -- (CRR) -- cycle;
\end{tikzpicture}
\end{figure}

@@

\begin{figure}
    \caption{Illustration of Lemma~\ref{lemma:stardivision}. Left: 
    the triangle $T = [ v_0, v_1, v_2 ]$ is bisected at the edge $S = [ v_0, v_1 ]$, leading to two new triangles. 
    The height vector to $v_2$ in all three triangles remains the same. The height vector to $z_S$ in the new triangle $[z_S, v_1, v_2]$ is one half of the height vector to $v_0$ in the original triangle. 
    Right: 
    the triangle $T$ is trisected, leading to three new triangles. 
    The height vector to $z_T$ from the opposite edge in any triangle is one third of the original height vector of that edge.}
    \begin{center}
    \begin{tikzpicture}
        % Coordinates of the triangle
        \coordinate (A) at (0,0); % Vertex A = v_0
        \coordinate (B) at (4,0); % Vertex B = v_1
        \coordinate (C) at (1,3); % Vertex C = v_2
        \coordinate (M) at ($(A)!0.5!(B)$); % Midpoint M of AB
        % Heights from each vertex
        \coordinate (H_A) at ($(C)!(A)!(B)$); % Height from A to BC
        \coordinate (H_B) at ($(C)!(B)!(A)$); % Height from B to AC
        \coordinate (H_C) at ($(A)!(C)!(B)$); % Height from C to AB
        \coordinate (H_M) at ($(B)!(M)!(C)$); % Height from M to BC
        % Drawing the triangle
        \draw[thick] (A) -- (B) -- (C) -- cycle;
        % Drawing the bisector from C to AB and the height vectors 
        %\draw[dashed] (C) -- (M);
        \draw[] (C) -- (M);
        \draw[dashed,->,line width=1.0pt,>=latex] (H_A) -- (A); % Height vector from A, original 
        \draw[dashed,->,line width=1.0pt,>=latex] (H_M) -- (M); % Height vector from A, original 
        \draw[dashed,->,line width=1.0pt,>=latex] (H_C) -- (C); % Height vector from C, unaffected
        % Marking the height points
        \node[above right] at (C) {$v_2$};  
        \node[below left] at (A) {$v_0$};
        \node[below right] at (B) {$v_1$};
        \node[below] at (M) {$z_S$};
    \end{tikzpicture}
    \begin{tikzpicture}

@@

        % Marking the points
        \node[above right] at (C) {$v_2$};  
        \node[below left] at (A) {$v_0$};
        \node[below right] at (B) {$v_1$};
        \node[right] at (G) {$z_T$};
    \end{tikzpicture}
    \end{center}
\end{figure}

@@

\begin{figure}[t]
    \caption{Sketch of the geometric situation in the proof of Proposition~\ref{proposition:starreflection}.
    The triangle $T$ completes the star around an interior vertex. $A$ is the complement of the triangle within the star. 
    $\Gamma_1$ is the interface between the two sets, and left invariant by the reflection.
    $\Gamma_2$ is left invariant by the deformation.
    $\Xi_{1}$ maps $T$ into $A$ while preserving the interface $\Gamma_1$,
    and 
    $\Xi_{2}$ maps the whole patch into $A$ while preserving the boundary $\Gamma_2$.
    }\label{figure:geometricconstruction}
    \centering
    \begin{tabular}{ccc}
    \begin{tikzpicture}
        % [line join=bevel,z={( 3.85mm, -3.85mm)}]
        [line join=bevel,x={( 1.5cm, 0mm)},y={( 0mm, 1.5cm)},z={( 1.5*3.85mm, -1.5*3.85mm)}]

@@

        \draw[dotted] (O) -- (A); % THIS ONE 
        \draw[dotted] (O) -- (B); % THIS ONE 
        \draw[] (A) -- (B); % THIS ONE 
%                 \draw (O) -- (C);
%                 \draw (O) -- (D);
%                 \draw (O) -- (E);
        \draw[line width=0.2em] (B) -- (C) -- (D) -- (E) -- (A);
    \end{tikzpicture}%
    \end{tabular} 
\end{figure}

@@

\begin{table}[t]
    \caption{
    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
    where boundary conditions are imposed along the boundary part $\Gamma$, 
    computed via lowest-order finite element methods on a refined mesh. 
    Notably, the top-left should and the bottom-right should asymptotically coincide, as should the bottom-left and the top-right.
    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} and Remark~\ref{remark:mixedbconsimplex:exteriorderivative:hilbert} 
    give the upper bound $2/\pi \cdot \diam(\Delta^3) \approx 0.90031631615$.
    }\label{table:referencepoincarefriedrichs}
    \centering
    \begin{tabular}{|l|c|c|c|}
        \hline
                                                  & $\grad$           & $\curl$           & $\divergence$   \\ \hline
        $\Gamma = F_0 \cup F_1 \cup F_2 \cup F_3$ & 0.0862501765      & 0.1453729386      & 0.2601720480    \\ \hline
        $\Gamma =          F_1 \cup F_2 \cup F_3$ & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
        $\Gamma =                   F_2 \cup F_3$ & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
        $\Gamma =                            F_3$ & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
        $\Gamma =                      \emptyset$ & 0.2631059409      & 0.1458215887      & 0.0874066554    \\ \hline
    \end{tabular}
\end{table}

@@

\begin{table}[t]
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 2D domains.
    Reference values for the gradient and divergence (2nd and 7th column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column), 
    and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (8th and 9th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates2D}
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est & $\grad$ ratio       & $\grad$ est   & $\grad$ ratio      & $\divergence$ ref  & $\divergence$ est  & $\divergence$ ratio \\ 
        \hline
        $\calT_{Q}$     & 0.318        & 0.904       & 2.842               & 0.904         & 2.842              & 0.225              & 1.339              &  5.953         \\
        \hline
        $\calT_{L}$     & 0.822        & 2.381       & 2.896               & 1.421         & 1.729              & 0.322              & 2.505              &  7.781         \\
        \hline
        $\calT_{L'}$    & 0.822        & 2.391       & 2.909               & 2.391         & 2.909              & 0.322              & 4.053              & 12.587         \\
        \hline
        $\calT_{S,5}$   & 0.978        & 2.752       & 2.814               & 1.779         & 1.819              & 0.346              & 3.717              & 10.744         \\ 
        \hline % centered
        $\calT_{S'}$    & 0.978        & 3.131       & 3.202               & 3.131         & 3.202              & 0.346              & 5.453              & 15.762         \\
        \hline % non-centered
        $\calT_{S''}$   & 0.978        & 2.761       & 2.824               & 2.761         & 2.824              & 0.346              & 4.662              & 13.476         \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{table}[t]
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants of the gradient over various triangulated 3D domains.
    Reference values for the gradient (2nd column) computed with finite element methods together with estimates and ratios: 
    Theorem~\ref{theorem:poincarefriedrichsestimate:grad} (3rd and 4th column), and using Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=0$ (5th and 6th column).
    }\label{table:estimates3D:grad}
    \centering
    \begin{tabular}{|r||r|r|r|r|r||r|r|r|}
        \hline
                        & $\grad$ ref  & $\grad$ est  & $\grad$ ratio       & $\grad$ est  & $\grad$ ratio  \\
        \hline
        $\calT_{C,5}$   & 0.317        & 4.317        & 13.581              & 3.246        & 10.214         \\
        \hline
        $\calT_{C,K}$   & 0.317        & 3.571        &  11.23              & 11.034       & 34.722         \\
        \hline
        $\calT_{B,5}$   & 1.022        & 7.698        & 7.5285              & 25.972       & 25.397         \\
        \hline
        $\calT_{B,K}$   & 1.022        & 10.106       & 9.8824              & 53.763       & 52.573         \\
        \hline
        $\calT_{F}$     & 0.711        & 10.622       & 14.927              &  268.071     & 377.033        \\ 
        \hline
    \end{tabular} 
\end{table}

\begin{table}[t]  
    \caption{
    Estimates for $L^2$ Poincar\'e--Friedrichs constants over various triangulated 3D domains.
    Reference values for the curl and divergence (2nd and 5th column) computed with finite element methods together with estimates and ratios
    that rely on Theorem~\ref{theorem:poincarefriedrichsestimate:exterior} with $k=1$ (3rd and 4th column) and with $k=2$ (5th and 6th column).
    Note that the divergence constant can always be estimated using Lemma~\ref{lemma:mixedbconsimplex}.
    }\label{table:estimates3D:curldiv}
    \centering
    \begin{tabular}{|r||r|r|r||r|r|r|}
        \hline
                        & $\curl$ ref  & $\curl$ est & $\curl$ ratio          & $\divergence$ ref & $\divergence$ est & $\divergence$ ratio \\ 
        \hline
        $\calT_{C,5}$   & 0.225        & 141.148     & 627.310                & 0.183             & 3.391             & 18.453          \\
        \hline
        $\calT_{C,K}$   & 0.225        & 12.157      & 54.030                 & 0.183             & 25.899            & 140.920         \\
        \hline
        $\calT_{B,5}$   & 0.331        & 113.084     & 341.056                & 0.233             & 152.886           & 655.993         \\
        \hline
        $\calT_{B,K}$   & 0.331        & 162.687     & 490.655                & 0.233             & 512.273           & 2198.026        \\
        \hline
        $\calT_{F}$     & 0.554        & 25752.342   & 46403.302              & 0.310             & 8958.467          & 28835.266       \\ 
        \hline
    \end{tabular}
\end{table}
